PanLex-RDF

### 2013-01-02 paper/2012/SWJ-PanLex/paper.tex

%patrick.westphal@studserv.uni-leipzig.de
%\author[1]{\fnms{Patrick} \snm{Westphal}},
%\author[1]{\fnms{Claus} \snm{Stadler}},
%\author[2]{\fnms{Jonathan} \snm{Pool}}
%\address[1]{University of Leipzig, Institute of Computer Science, AKSW}
%\address[2]{TODO}

@@

An overview of the number of instances per entity in the current PanLex database is given in~\autoref{fig:plx-entity-counts}.
\begin{table}
\centering
\begin{scriptsize}
\begin{tabular}{lr}
\toprule
Entity & Instances \\
%\midrule
Expressions & 18,580,594 \\ % SELECT COUNT(ex) FROM ex;
%\midrule
Languages   & 7,839 \\ % SELECT COUNT(lc) FROM lc; -- all language codes (ISO 639-3, ISO 639-2, ISO 639-5) known in the PanLex db
% FIXME: there should not be more languages than language varieties
%\midrule
Language Varieties & 7,248 \\ % SELECT COUNT(lv) FROM lv;
%\midrule
Meanings    & 20,023,427 \\ % SELECT COUNT(mn) FROM mn;
%\midrule
Definitions & 2,522,605 \\ % SELECT COUNT(df) FROM df;
%\midrule
Denotations & 50,803,243 \\ % SELECT COUNT(dn) FROM dn;
%\midrule
Users       & 7 \\ % SELECT COUNT(us) FROM us;
%\midrule
Licenses    & 10 \\ % SELECT COUNT(li) FROM apli;
\bottomrule
\end{tabular}
\end{scriptsize}
\caption{Number of entities in the PanLex database}
\label{fig:plx-entity-counts}
\end{table}

@@

\item The RDF analog of the PanLex \emph{meaning} is the \texttt{plx:Meaning}.
Entities of this class may have an identifier assigned with the
\texttt{plx:identifier} property pointing to an \texttt{xsd:string} literal.
This meaning identifier represents ids given to the considered meaning in other
data sources and may at a later stage be used to build links to the meaning
as represented on these sites.
Meanings may also have \emph{definitions}, entities of the
\texttt{plx:Definition} class, giving a textual representation
(\texttt{rdfs:label}) with more than just a lexeme in a certain
language variety (\texttt{plx:languageVariety}).

>>>>

%patrick.westphal@studserv.uni-leipzig.de
\author[1]{\fnms{Patrick} \snm{Westphal}},
\author[2]{\fnms{Claus} \snm{Stadler}},
\author[3]{\fnms{Jonathan} \snm{Pool}}
\address[1]{University of Leipzig, patrick.westphal@studserv.uni-leipzig.de}
\address[2]{University of Leipzig, cstadler@informatik.uni-leipzig.de}
\address[3]{Long Now Foundation, San Francisco, pool@utilika.org}

%\author[1]{Author A\thanks{A.A@university.edu}}
%\author[1]{Author B\thanks{B.B@university.edu}}
%\author[1]{Author C\thanks{C.C@university.edu}}
%\author[2]{Author D\thanks{D.D@university.edu}}
%\author[2]{Author E\thanks{E.E@university.edu}}
%\affil[1]{Department of Computer Science, \LaTeX\ University}
%\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}

%\address[1]{University of Leipzig, Institute of Computer Science, AKSW, patrick.westphal@studserv.uni-leipzig.de}

@@

An overview of the number of instances per entity in the current PanLex database is given in~\autoref{fig:plx-entity-counts}.
\begin{table}
\centering
\begin{scriptsize}
\begin{tabular}{lr}
\toprule
Entity & Instances \\
%\midrule
Approvers & 3,905 \\ % SELECT COUNT(ex) FROM ex;
Expressions & 18,580,594 \\ % SELECT COUNT(ex) FROM ex;
%\midrule
Languages   & 7,839 \\ % SELECT COUNT(lc) FROM lc; -- all language codes (ISO 639-3, ISO 639-2, ISO 639-5) known in the PanLex db
% FIXME: there should not be more languages than language varieties
%\midrule
Language Varieties & 7,248 \\ % SELECT COUNT(lv) FROM lv;
%\midrule
Meanings    & 20,023,427 \\ % SELECT COUNT(mn) FROM mn;
%\midrule
Definitions & 2,522,605 \\ % SELECT COUNT(df) FROM df;
%\midrule
Denotations & 50,803,243 \\ % SELECT COUNT(dn) FROM dn;
%\midrule
Users       & 7 \\ % SELECT COUNT(us) FROM us;
%\midrule
Licenses    & 10 \\ % SELECT COUNT(li) FROM apli;
\bottomrule
\end{tabular}
\end{scriptsize}
\caption{Number of entities in the PanLex database}
\label{fig:plx-entity-counts}
\end{table}

@@

\item The RDF analog of the PanLex \emph{meaning} is the \texttt{plx:Meaning}.
Entities of this class may have an identifier assigned with the
\texttt{plx:identifier} property pointing to an \texttt{xsd:string} literal.
%This meaning identifier represents ids given to the considered meaning in other
%data sources and may at a later stage be used to build links to the meaning
%as represented on these sites.
Meanings may also have \emph{definitions}, entities of the
\texttt{plx:Definition} class, giving a textual representation
(\texttt{rdfs:label}) with more than just a lexeme in a certain
language variety (\texttt{plx:languageVariety}).
